Dynamic RB scheduling for different slices of eMBB and URLLC in the O-RAN system \vspace{-.1cm}

### 2022-06-06 Latex/journal_v2/version5/pr.tex
change paper after revision

\begin{subequations} \label{mainP}
\begin{alignat}{4}
\max\limits_{ \boldsymbol{E}, \boldsymbol{X},\boldsymbol{M}, \boldsymbol{P} } &  \sum_i {\mathcal{R}}_{i}^e(t) - \eta \sum_j T^{\text{tot}, u}(t)       \ \\
\text{subject to} \quad  & {\mathcal{R}}_{i}^e(t) \geq  \mathcal{R}_{min}^e \quad \forall i \in \mathcal{U}_e, \label{p1} \\
& \sum_k^K \sum_i^{U_e} p^k_i(t) \leq P_{\text{max}},  \label{p1-1} \\ 
& Pr\{\bar{\mathcal{R}}_{i}^e(t) \leq {R}_{min}^e\}  \leq \epsilon,\quad \forall i \in \mathcal{U}_e, \label{p2}\\
&T^{\text{tot}, e}_i(t)  \leq T_{min}^e  \quad \forall i \in \mathcal{U}_e, \label{p2-1} \\
&T^{\text{tot}, u}_j(t)  \leq T_{min}^u  \quad \forall j \in \mathcal{U}_u, \label{p3} \\
& \bar{\mathcal{R}}_{j}^u(t) \geq  \mathcal{R}_{min}^u \quad \forall j \in \mathcal{U}_u, \label{p3-1} \\
&Pr\{T^{\text{RU}, u}_j(t) \geq T_{min}^u\} \leq \epsilon  \quad \forall j \in \mathcal{U}_u, \label{p4} \\
&\sum_{i=1}^{U_1}e^k_i(t)\leq 1 \quad \forall k \in \{1,...,K\},\label{p5} \\
&e^k_i(t)\in \{0,1\}  \quad \forall i,k, \label{p6} \\
& x^k_i(t)\in \{0,1,...,L\}  \quad \forall i,k, \label{p7} \\
& \mu^l_s \geq \alpha_s/M^l_s \quad l \in \{c,d\}, s\in\{e,u\}, \label{p8} \\
& {\mathcal{R}}^s(t) \geq {\lambda}_{\mathfrak{i},s}^u(t) \quad \forall \mathfrak{i} \in \mathcal{U}_s, s\in \{e,u\}\label{p9} \\
& 0 \leq M^l_e  + M^l_u \leq M_{max}^l  \quad l \in \{c,d\},\label{p10}
\end{alignat}
\label{constraints}
\end{subequations}
Where, \eqref{p1}, guarantees the minimum data rate of eMBB UEs, also \eqref{p1-1} indicates the power allocation constraints.
\eqref{p2}, supports the reliability of eMBB while puncturing the URLLC. Moreover, \eqref{p2-1} indicates the maximum delay that the eMBB service can tolerate.
In addition, \eqref{p3}, \eqref{p3-1} and \eqref{p4} guarantee the latency, the minimum data rate and reliability of URLLC UEs, respectively.
Furthermore, eMBB RB allocation constraint is indicated by \eqref{p5}, and \eqref{p6}.
\eqref{p7}, indicate that the punctured mini-time slot are fewer than the total number of mini-slots in the RB.
\eqref{p8} and \eqref{p9} denotes the stability of the M/M/1 queue model.
\eqref{p10} restricts the number of VNF in each slice due to the limited resources.

\section{Proposed Algorithm}
In this section, we are talking about our proposed algorithm to solve the problem \eqref{mainP}.
Since this problem is mixed-integer nonlinear programming (MINLP) with binary and integer variables, it is complicated to solve. Also, this is a two-time scale problem.
Therefore, We need to solve this problem on a two-time scale. On a large time scale, the problem of assigning RB to eMBB service is obtained and then the power allocation is performed. 
Moreover, in this time scale, we can estimate the optimal number of VNFs for each service, and in the small time scale, the problem of URLLC puncturing is solved. 
\subsection{Large time scale}
In this time scale, we want to solve the problem of eMBB scheduling, power allocation, and finding the optimal number of VNF for each service.
Here, we suppose the puncturing of URLLC is fixed, hence, we want to solve the problem \eqref{mainP}.
The problem \eqref{mainP}, is altered to the following problem

\begin{subequations} \label{mainP1}
\begin{alignat}{4}
\max\limits_{ \boldsymbol{E},\boldsymbol{M}, \boldsymbol{P}} &  \sum_i {\mathcal{R}}_{i}^e(t) - \eta T^{\text{proc}, u}(t)       \ \\
\text{subject to} \quad  & \bar{\mathcal{R}}_{i}^e(t) \geq  \mathcal{R}_{min}^e \quad \forall i \in \mathcal{U}_1, \label{p11} \\
& \sum_k^K \sum_i^{U_e} p^k_i(t) \leq P_{\text{max}},  \label{p11-1} \\
& Pr\{\bar{\mathcal{R}}_{i}^e(t) \leq {R}_{min}^e\}  \leq \epsilon,\quad \forall i \in \mathcal{U}_1, \label{p12}\\
&T^{\text{tot}, e}_i(t)  \leq T_{min}^e  \quad \forall i \in \mathcal{U}_e, \label{p12-1} \\
&T^{\text{process}, u}_i(t)  \leq T_{\text{process,min}}^u  \quad \forall i \in \mathcal{U}_u, \label{p12-2} \\
&\sum_{i=1}^{U_1}e^k_i(t)\leq 1 \quad \forall k \in \{1,...,K\},\label{p15} \\
&e^k_i(t)\in \{0,1\}  \quad \forall i,k, \label{p16} \\
& \mu^l_s \geq \alpha_s/M^l_s \quad l \in \{c,d\}, s\in\{e,u\},\label{p18} \\
& 0 \leq M^l_e  + M^l_u \leq M_{max}^l  \quad l \in \{c,d\},\label{p110}
\end{alignat}
\label{constraints}
\end{subequations}

@@

The problem \eqref{mainP1}, is still mixed integer non-linear programming (MINP). Here, the problem \eqref{mainP1}
can also be decomposed into two sub-problems which is depicted as follow.
\subsubsection{sub-problem 1}
In this section, we want to solve the sub-problem of RB allocation of eMBB UEs.
The problem can be written as follow.
\begin{subequations} \label{mainP11}
\begin{alignat}{4}
\max\limits_{ \boldsymbol{E} } &  \sum_i \bar{\mathcal{R}}_{i}^e(t)       \ \\
\text{subject to} \quad  & \bar{\mathcal{R}}_{i}^e(t) \geq  \mathcal{R}_{min}^e \quad \forall i \in \mathcal{U}_1, \label{p11} \\
&\sum_{i=1}^{U_1}e^k_i(t)\leq 1 \quad \forall k \in \{1,...,K\},\label{p115} \\
&e^k_i(t)\in \{0,1\}  \quad \forall i,k, \label{p116} 
\end{alignat}
\label{constraints}
\end{subequations}
\subsubsection{sub-problem 2}
In this section, we want to solve the sub-problem of finding the optimal number of VNF for URLLC services.
The problem is formulated as follow.
\begin{subequations} \label{mainP2}
\begin{alignat}{4}
\min\limits_{ \boldsymbol{M} } &  T^{\text{proc}, u}(t)       \ \\
\text{subject to} \quad  & \mu^l \geq \alpha/M^l \quad l \in \{c,d\},\label{p28} \\
& 0 \leq M^l \leq M_{max}^l  \quad l \in \{c,d\},\label{p210}
\end{alignat}
\label{constraints}
\end{subequations}
\subsection{Small time scale}
In the small time scale, we assume that the eMBB RB allocation is performed and the optimal number of VNF for URLLC is obtained. Therefore, the problem of puncturing URLLC UEs is performed.
\begin{subequations} \label{mainP2}
\begin{alignat}{4}
\min\limits_{  \boldsymbol{\Psi} } &  \sum_j T^{RU, u}(t)       \ \\
\text{subject to} \quad  &T^{\text{tot}, u}_j(t)  \leq T_{min}^u  \quad \forall j \in \mathcal{U}_2, \label{p33} \\
& Pr\{\bar{\mathcal{R}}_{i}^e(t) \leq {R}_{min}^e\}  \leq \epsilon,\quad \forall i \in \mathcal{U}_1, \label{p32}\\
&Pr\{T^{\text{RU}, u}_j(t) \geq T_{min}^u\} \leq \epsilon  \quad \forall j \in \mathcal{U}_2, \label{p34} \\
& 0 \leq n^k_i(t)\leq 1  \quad \forall i,k, \label{p37} \\
& \bar{\mathcal{R}}^u(t) \geq {\lambda}_{j}^u(t) \quad \forall j \in \mathcal{U}_2,\label{p39} 
\end{alignat}
\label{constraints}
\end{subequations}

>>>>

\begin{subequations} \label{mainP}
\begin{alignat}{4}
\max\limits_{ \boldsymbol{E}, \boldsymbol{X},\boldsymbol{M}, \boldsymbol{P} } &  \sum_i {\mathcal{R}}_{i}^e(t) - \eta \sum_j T^{\text{tot}, u}(t)       \ \\
\text{subject to} \quad  & {\mathcal{R}}_{i}^e(t) \geq  \mathcal{R}_{min}^e \quad \forall i \in \mathcal{U}_e, \label{p1} \\
& \sum_k^K \sum_i^{U_e} p^k_i(t) \leq P_{\text{max}},  \label{p1-1} \\ 
& Pr\{{\mathcal{R}}_{i}^e(t) \leq {R}_{min}^e\}  \leq \epsilon,\quad \forall i \in \mathcal{U}_e, \label{p2}\\
&T^{\text{tot}, e}_i(t)  \leq T_{min}^e  \quad \forall i \in \mathcal{U}_e, \label{p2-1} \\
&T^{\text{tot}, u}_j(t)  \leq T_{min}^u  \quad \forall j \in \mathcal{U}_u, \label{p3} \\
& {\mathcal{R}}_{j}^u(t) \geq  \mathcal{R}_{min}^u \quad \forall j \in \mathcal{U}_u, \label{p3-1} \\
&Pr\{T^{\text{RU}, u}_j(t) \geq T_{min}^u\} \leq \epsilon  \quad \forall j \in \mathcal{U}_u, \label{p4} \\
&\sum_{i=1}^{U_1}e^k_i(t)\leq 1 \quad \forall k \in \{1,...,K\},\label{p5} \\
&e^k_i(t)\in \{0,1\}  \quad \forall i,k, \label{p6} \\
& x^k_i(t)\in \{0,1,...,L\}  \quad \forall i,k, \label{p7} \\
& \mu^l_s \geq \alpha_s/M^l_s \quad l \in \{c,d\}, s\in\{e,u\}, \label{p8} \\
& {\mathcal{R}_{\mathfrak{i}}}^s(t) \geq {\lambda}_{\mathfrak{i},s}(t) \quad \forall \mathfrak{i} \in \mathcal{U}_s, s\in \{e,u\}\label{p9} \\
& 0 \leq M^l_e  + M^l_u \leq M_{max}^l  \quad l \in \{c,d\},\label{p10}\\
& 0 \leq M^l_e, M^l_u  \quad l \in \{c,d\},\label{p011}
\end{alignat}
\label{constraints}
\end{subequations}
Where, \eqref{p1}, guarantees the minimum data rate of eMBB UEs, also \eqref{p1-1} indicates the power allocation constraints.
\eqref{p2}, supports the reliability of eMBB while puncturing the URLLC. Moreover, \eqref{p2-1} indicates the maximum delay that the eMBB service can tolerate.
In addition, \eqref{p3}, \eqref{p3-1} and \eqref{p4} guarantee the latency, the minimum data rate and reliability of URLLC UEs, respectively.
Furthermore, eMBB RB allocation constraint is indicated by \eqref{p5}, and \eqref{p6}.
\eqref{p7}, indicate that the punctured mini-time slot are fewer than the total number of mini-slots in the RB.
\eqref{p8} and \eqref{p9} denotes the stability of the M/M/1 queue model.
\eqref{p10}, and \eqref{p011} restricts the number of VNF in each slice due to the limited resources.

\section{Proposed Algorithm}
In this section, we are talking about our proposed algorithm to solve the problem \eqref{mainP}.
Since this problem is mixed-integer nonlinear programming (MINLP) with binary and integer variables, it is NP-hard and complicated to solve. Also, this is a two-time scale problem.
Therefore, We need to solve this problem on a two-time scale. On a large time scale, the problem of assigning RB to eMBB service is obtained and then the power allocation is performed. 
Moreover, in this time scale, we can estimate the optimal number of VNFs for each service, and in the small time scale, the problem of URLLC puncturing is solved. 
\subsection{Large time scale}
In this time scale, we want to solve the problem of eMBB scheduling, power allocation, and finding the optimal number of VNF for each service.
Here, we suppose the puncturing of URLLC is fixed, hence, we want to solve the problem \eqref{mainP}.
The problem \eqref{mainP}, is altered to the following problem

\begin{subequations} \label{mainP1}
\begin{alignat}{4}
\max\limits_{ \boldsymbol{E},\boldsymbol{M}, \boldsymbol{P}} &  \sum_i {\mathcal{R}}_{i}^e(t) - \eta T^{\text{proc}, u}(t)       \\
\text{subject to} \quad  &\eqref{p1}, \eqref{p1-1}, \eqref{p2}, \eqref{p2-1}, \eqref{p5}, \eqref{p6}, \eqref{p8},\\
& {\mathcal{R}}^e(t) \geq {\lambda}_{\mathfrak{i},e}(t) \quad \forall \mathfrak{i} \in \mathcal{U}_e,\\
& \eqref{p10}, \eqref{p011},
\end{alignat}
\label{constraints}
\end{subequations}

@@

The problem \eqref{mainP1}, is still mixed integer non-linear programming (MINP). Here, the problem \eqref{mainP1}
can be decomposed into two sub-problems which is depicted as follow. In this first sub-problem, we assume that the channel gain is not known, and we aim to obtain the optimal number of VNFs and RB allocation to the eMBB service. In the second sub-problem, we know the channel gain with error ($h = h + \Delta h$), and we want to obtain the power allocation.
\subsubsection{eMBB RB Allocation and VNF Assignment}
In this section, we want to solve the sub-problem of RB allocation of eMBB service and find the optimal number of VNFs for each service.
The problem can be written as follow.
\begin{subequations} \label{mainP11}
\begin{alignat}{4}
\max\limits_{ \boldsymbol{E}, \boldsymbol{M} } &  \sum_i \bar{\mathcal{R}}_{i}^e(t) -T^{\text{proc}, u}(t)      \ \\
\text{subject to} \quad  & \bar{\mathcal{R}}_{i}^e(t) \geq  \mathcal{R}_{min}^e \quad \forall i \in \mathcal{U}_e, \label{pp11} \\
&\bar{T}^{\text{tot}, e}_i(t)  \leq T_{min}^e  \quad \forall i \in \mathcal{U}_e, \label{p112-1} \\
%&T^{\text{proc}, u}_j(t)  \leq T_{\text{proc,min}}^u  \quad \forall j \in \mathcal{U}_u, \label{p112-2} \\
&\sum_{i=1}^{U_e}e^k_i(t)\leq 1 \quad \forall k \in \{1,...,K\},\label{p115} \\
&e^k_i(t)\in \{0,1\}  \quad \forall i,k, \label{p116} \\
& \mu^l_s \geq \alpha_s/M^l_s \quad l \in \{c,d\}, s\in\{e,u\},\label{p118} \\
& 0 \leq M^l_e  + M^l_u \leq M_{max}^l  \quad l \in \{c,d\},\label{p1110} \\
& 0 \leq M^l_e, M^l_u  \quad l \in \{c,d\},\label{p110}
\end{alignat}
\label{constraints}
\end{subequations}
The problem \eqref{mainP11}, can be decomposed into two subproblems using primal decomposition. $\boldsymbol{E}$
is the private variable and $\boldsymbol{M}$ is the decoupling variable.
Therefore, the first subproblem is 
\begin{subequations}
\begin{alignat}{4}
\max\limits_{ \boldsymbol{E}, M_e} &  \sum_i \bar{\mathcal{R}}_{i}^e(t) \\
\text{subject to} \quad  & \eqref{pp11},\eqref{p112-1}, \eqref{p115}, \eqref{p116},\\
& \mu^l_e \geq \alpha_e/M^l_e \quad l \in \{c,d\},\label{pp118} \\
& 0 \leq M^l_e \leq \tau
\end{alignat}
\end{subequations}
Moreover, the second subproblem is 
\begin{subequations}
\begin{alignat}{4}
\min\limits_{ M_u } &  T^{\text{proc}, u}(t) \\
\text{subject to} \quad & \mu^l_u \geq \alpha_s/M^l_u \quad l \in \{c,d\},\label{pp118} \\
& 0 \leq M^l_u \leq M_{max}^l -\tau
\end{alignat}
\end{subequations} 
\subsubsection{eMBB Power Allocation}
In this section, we want to solve the sub-problem of power allocation for eMBB UEs.
The problem is formulated as follow.
\begin{subequations} \label{mainP12}
\begin{alignat}{4}
\max\limits_{ \boldsymbol{P} } &  \sum_i {\mathcal{R}}_{i}^e(t)       \ \\
\text{subject to} \quad  & \eqref{p1-1}, \eqref{p2}, \eqref{p2-1},
\end{alignat}
\label{constraints}
\end{subequations}
\subsection{Small time scale}
In the small time scale, we assume that the eMBB RB allocation is performed and the optimal number of VNF for URLLC is obtained. Therefore, the problem of puncturing URLLC UEs is considered.
\begin{subequations} \label{mainP2}
\begin{alignat}{4}
\min\limits_{  \boldsymbol{X} } &  \sum_j T^{RU, u}(t)       \ \\
\text{subject to} \quad & Pr\{{\mathcal{R}}_{i}^e(t) \leq {R}_{min}^e\}  \leq \epsilon_2,\quad \forall i \in \mathcal{U}_e, \label{p32}\\
&Pr\{T^{\text{tot}, u}_j(t) \geq T_{min}^u - T^{\text{proc}}\} \leq \epsilon_3  \quad \forall j \in \mathcal{U}_u, \label{p34} \\
& x^k_i(t)\in \{0,1,...,L\}  \label{p37} \\
& {\mathcal{R}_j}^u(t) \geq {\lambda}_{j}^u(t) \quad \forall j \in \mathcal{U}_u,\label{p39} 
\end{alignat}
\label{constraints}
\end{subequations}
